---
title: "Ford Stat Project"
author: "Kasthuri Raja"
date: "2 June 2022"
output:
  html_document: default
  pdf_document: default
---

```{r}
Ford <- read.csv(file.choose(), header = T)

```

Attribute Information:

1.model - > Ford Car Brands

2.year - >Production Year

3.price - >Price of car in $

4.transmission - > Automatic,Manual, Semi-Auto

5.mileage -> Number of miles traveled

6.fuel_Type -> Petrol,Diesel,Hybrid,Electric,Other

7.tax -> Annual Tax

8.mpg - > Miles per Gallon

9.engineSize - > Car's Engine Size

```{r}
dim(Ford)
head(Ford, n=10)
tail(Ford)
str(Ford)
```

```{r}
summary(Ford)
```



Displaying the values of the selected variables 


```{r}
table(Ford$transmission)

```

```{r}
table(Ford$model)
```

```{r}
table(Ford$fuelType)
```

Displaying the Chart

In this Chart The Price Has Been Given in Dollars
```{r}

hist(Ford$price)
```
```{r}
mean(Ford$price)
```
In this Chart The mpg Say that How many Mileage does the Car give.for an approximate result, we divide the fuel economy value by 2.352 to get in kilometer per litre.

```{r}
hist(Ford$mpg)
```


```{r}
mean(Ford$mpg)
```
In this Chart the mileage says that how many miles does the car travelled 
```{r}
hist(Ford$mileage)
```
```{r}
hist(Ford$engineSize)
```
```{r}
hist(Ford$year)
```


```{r}
boxplot(Ford$price~Ford$year)
```


```{r}
boxplot(Ford$tax)
```
```{r}

boxplot(Ford$price ~ Ford$transmission)
```
```{r}

boxplot(Ford$mileage)
```
```{r}

boxplot(Ford$year)
```
```{r}

boxplot(price ~ fuelType ,data = Ford)
```

```{r}
barplot(table(Ford$mpg,Ford$fuelType),beside=TRUE)
```


```{r}
table(Ford$model)
```

```{r}

barplot(table(Ford$transmission, Ford$fuelType),beside = TRUE,legend.text = rownames(table(Ford$transmission)))
```

```{r}

barplot(table(Ford$transmission=="Automatic",Ford$model),beside = TRUE)
```

```{r}

barplot(table(Ford$fuelType),beside = TRUE)
```

```{r}

Ford_sub<- subset(Ford, model =="Fiesta", select = c("model","transmission","fuelType","price","year","mpg"))
Ford_sub
```

